INTELLIGENT SYSTEMS

### 2021-04-21 slides/slides_paper1.tex
add 1 slide to paper1

\begin{frame}[t]{EXPERIMENTS}
    The results obtained on different datasets \footfullcite{PASCAL-S, ECSSD, ASD}, were compared with those 
    btained by the systems already existing at the state of the art.
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8 \linewidth]{/paper1/metrics.png}
        \centering
        \caption{Metrics comparison.}
        \label{fig: metrics}
    \end{figure}
\end{frame}

>>>>

\begin{frame}{EXPERIMENTS - Fixation Prediction}
    The fixation prediction indicates the likelihood with which a human is 
    looking at a given position in the scene. There are several metrics that are 
    used to evaluate the prediction such as Natural Scanpath Saliency (NSS) 
    and ROC (AUC). In the following article the ROC method is mainly used, 
    on three types of datasets, to compare the proposed system with others already 
    existing at the state of the art, as shown in Fig. \ref{fig: ROC}.
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper1/ROC.png}
        \centering
        \caption{ROC comparison.}
        \label{fig: ROC}
    \end{figure}
    The computation of the CBSP takes into account this {\bfseries{center bias}}, 
    without however losing the information on the other objects in the scene.
\end{frame}

\begin{frame}[t]{EXPERIMENTS - Salient Object Detection}
    To compare the performance of the salient object detection, metrics such 
    as Precision, Recall, F-score, Weighted F-score and MAE (Mean Absolute 
    Error) were used. In precision and recall, HS and RF are the best, but in 
    the F-score, CGVS($t_2$) whit center bias, is best. Without center bias, CGVS 
    would achieve lower performance (CGVS'').
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8 \linewidth]{/paper1/metrics.png}
        \centering
        \caption{Metrics comparison.}
    \end{figure}
\end{frame}
